Timely Object Recognition

### 2012-06-01 writeups/nips12/evaluation.tex
trajectories figure in

\begin{figure}[h!]
\centering
\subfloat[Occurence of a class with another]{\includegraphics[]
    {../figures/full_pascal_trainval_stats/cooccur_trim.png}} \hfill
\subfloat[Occurence of a class with two others]{\includegraphics[]
    {../figures/full_pascal_trainval_stats/cooccur_second_order_trim.png}}
  \caption{
  Co-occurrence statistics on the training portion of the PASCAL VOC 2007 dataset.
  In the first plot, a (row,column) cell shows the probability that an image that contains an object of the row class also contains an object of the column class.
  Accordingly, in the second plot, the probability that an image containing objects of the two classes listed in the row also contains an object of the column class.
  }
  \label{fig:dataset_stats}
\end{figure}

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{\includegraphics[width=0.47\linewidth]
    {../figures/final1_515.png}} \hfill
\subfloat[Execution traces of different policies]{\includegraphics[draft,width=0.47\linewidth]
    {../figures/final1.png}}
 \label{fig:results1}
\end{figure}

@@

>>>>

\begin{figure}[h!]
\centering
\subfloat[AP vs. Time curves for Random, Oracle, the Fixed Order baseline, and our best-performing policy, with start time of 5 seconds and deadline of 15 seconds.]{
\includegraphics[width=0.47\linewidth]
    {../figures/final1_515.png}\label{fig:results1}} \hfill
\subfloat[Reward function explanation]{
\includegraphics[width=0.47\linewidth]
    {../figures/apvst_expl.pdf}\label{fig:rewards}}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.86\linewidth]{../figures/trajectories.pdf}
  \caption{\todo{trajectories}}
  \label{fig:trajectories}
\end{figure}

### 2012-06-01 writeups/nips12/technical.tex
trajectories figure in

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.56\linewidth]{../figures/apvst_expl.pdf}
  \caption{\todo{what text here?} A per-action greedy value function that corresponds to the maximization of our objective function is the area of the horizontal slice under the curve due to the action. The figure shows this analysis for the action highlighted in orange.}
  \label{fig:rewards}
\end{figure}

@@

\begin{figure}[h!]
\centering
\subfigure[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
\subfigure[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
\label{fig:weights}
\end{figure}

\subsection{Updating with observations} \label{sec:updating}
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.56\linewidth]{../figures/mrf_w_gist.pdf}
% \caption{
% \todo{get rid of this figure?}
% The MRF inference model used in our system. The shaded nodes represent two actions that have already been taken; their observations have been recorded.
% }
% \label{fig:model}
% \end{figure}

@@

We evaluate two approaches of updating probabilities: \emph{direct} and \emph{MRF}.
In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.

>>>>

@@

\begin{figure}[h!]
\centering
\subfloat[Greedy]{\includegraphics[width=0.49\linewidth]{../figures/weights_greedy}}
\subfloat[RL]{\includegraphics[width=0.49\linewidth]{../figures/weights_rl}}
% \includegraphics[width=0.87\linewidth]{../figures/weights.pdf}
\caption{Weights \todo{describe. can talk about the person-class weights, the role of the time weights. how you can see the co-occurrence matrix in the weights}}
\label{fig:weights}
\end{figure}

\subsection{Updating with observations} \label{sec:updating}

@@

We evaluate two approaches for updating probabilities: \emph{direct} and \emph{MRF}.
In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.
